04_DESeq_sexes

### 2019-07-19 analysis/04_DESeq2_sexes.Rmd
first pass a minipulate, don't like

```{r manipulation}

>>>>

```{r manipulationVcontrol}
versuscontrol <- c("control.m.inc.d3" , "control.m.inc.d8", "control.m.inc.d9", "control.m.inc.d17", 
                      "control.m.n2", "control.prolong", "control.extend")

manipulationVcontrol <- function(DEGs, mysubtitle, myfill){

  # subset to look within one tissue in one sex
  DEGs <- DEGs %>%
    dplyr::mutate(comparison = row.names(.)) %>%
    dplyr::filter(comparison %in% versuscontrol)

  DEGs$comparison <- factor(DEGs$comparison, levels = versuscontrol)

  mybarplot <- ggplot(DEGs, aes(comparison)) +
    geom_bar(aes(weight = V3), fill = myfill) +
    theme_minimal(base_size = 8) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(subtitle = mysubtitle, y = "Number of DEGs", x = NULL) +
    #ylim(0, 5105) +
    geom_line(aes(x=comparison, y=V3, group = 1))

  return(mybarplot)
}

g <- manipulationVcontrol(DEGs.female_hypothalamus, "Female hypothalamus", "#00A08A")
h <- manipulationVcontrol(DEGs.female_pituitary, "Female pituitary", "#00A08A")
i <- manipulationVcontrol(DEGs.female_gonad, "Female gonad", "#00A08A")
j <- manipulationVcontrol(DEGs.male_hypothalamus, "Male hypothalamus", "#F98400")
k <- manipulationVcontrol(DEGs.male_pituitary, "Male pituitary", "#F98400")
l <- manipulationVcontrol(DEGs.male_gondad, "Male gonad", "#F98400")

pdf("../figures/sexes/manipulationVcontrol-1.pdf", width = 10, height = 6)
plot(mybarplots)
dev.off()
